### 2020-05-07 README.Rmd
simplified readme style

<img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>

@@

AIMS Data Platform R Client
==========================

__AIMS Data Platform R Client__ will provide easy access to data sets for R applications to the [AIMS Data Platform API](https://aims.github.io/data-platform).

Usage of AIMS Data Platform API Key
----------------------------------

__AIMS Data Platform__ requires an API Key for requests, [get a key here.](https://aims.github.io/data-platform/key-request)

@@

```
AIMS_DATAPLATFORM_API_KEY=XXXXXXXXXXXXX

```
The `.Renviron` file is usually stored in each users home directory.

@@

Installation
------------

At this stage __AIMS Data Platform R Client__ is not hosted on CRAN R package network.
An alternative method of installation is to use the R `devtools` package.

@@

After `devtools` has been installed the __AIMS Data Platform R Client__ can be installed directly
from GitHub using the following command:

@@

Available Data Sets
-------------------

The __AIMS Data Platform API__ is a *REST API* providing *JSON* formatted data. Documentation about available data sets can be found on the [AIMS Data Platfom API](https://aims.github.io/data-platform).

Further Information
----------------

Further information about the __AIMS DataPlatform R Client__ and __AIMS DataPlatform API__ can be seen on the [project page](https://aims.github.io/data-platform-r).

>>>>

# dataaimsr <img src="man/figures/logo.png" width = 200 alt="dataaimsr Logo"/>

@@

## Overview

`dataaimsr` is the **AIMS Data Platform R Client** will provide easy access to data sets for R applications to the [AIMS Data Platform API](https://aims.github.io/data-platform).

### Usage of AIMS Data Platform API Key

**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://aims.github.io/data-platform/key-request)

@@

```
AIMS_DATAPLATFORM_API_KEY=XXXXXXXXXXXXX
```

The `.Renviron` file is usually stored in each users home directory.

@@

### Installation

At this stage **AIMS Data Platform R Client** is not hosted on CRAN R package network.
An alternative method of installation is to use the R `devtools` package.

@@

After `devtools` has been installed the **AIMS Data Platform R Client** can be installed directly
from GitHub using the following command:

@@

### Available Data Sets

The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data. Documentation about available data sets can be found on the [AIMS Data Platfom API](https://aims.github.io/data-platform).

### Further Information

Further information about the **AIMS DataPlatform R Client** and **AIMS DataPlatform API** can be seen on the [project page](https://aims.github.io/data-platform-r).
